Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-27 manuscript/cpcrw_manuscript.Rmd
Code and ms text summarizing DOC, C, N

@@

>>>>

TODO: look at Podrebarac (2016) - Soils isolated during incubation underestimate temperature sensitivity of respiration and its response to climate history

@@

Sample DOC was `r pn(cndata_summary["DOC_mg_kg_mean"], 2)` ± `r pn(cndata_summary["DOC_mg_kg_sd"], 2)` mg kg^-1^. Carbon content was `r pn(cndata_summary["C_percent_mean"], 2)`% ± `r pn(cndata_summary["C_percent_sd"], 2)`%, while N content was `r pn(cndata_summary["N_percent_mean"], 2)`% ± `r pn(cndata_summary["N_percent_sd"], 2)`%. Neither temperature was treatment exerted any significant effect on these properties (P > 0.1 for all).
